Testing and Isolation Efficacy: Insights from a Simple Epidemic Model

### 2021-04-16 SIR_manuscript.tex
minor edit

\begin{enumerate}
\item \label{p1:eta} increasing the isolation parameters for tested and confirmed individuals decreases \Rnum;
$$\partial{\Rnum}/\partial{\theta\_c} \leq 0 \text{~and~} \partial{\Rnum}/\partial{\theta\_w} \leq 0.$$ 
\item \label{p1:rho} a higher rate of testing may increase or decrease $\Rnum$;
$$\partial{\Rnum}/\partial{\rho}$$ \text{~can be positive or negative}.
\item \label{p1:omega} A higher rate of of test return may increase or decrease \Rnum.
$$\partial{\Rnum}/\partial{\omega} \text{~can be positive or negative}.$$
\end{enumerate}

>>>>

\begin{enumerate}
\item \label{p1:eta} increasing the isolation parameters for tested and confirmed individuals decreases \Rnum;
$$\partial{\Rnum}/\partial{\theta\_c} \leq 0 \text{~and~} \partial{\Rnum}/\partial{\theta\_w} \leq 0.$$ 
\item \label{p1:rho} a higher rate of testing may increase or decrease $\Rnum$;
$$\partial{\Rnum}/\partial{\rho} \text{~can be positive or negative}.$$
\item \label{p1:omega} A higher rate of of test return may increase or decrease \Rnum.
$$\partial{\Rnum}/\partial{\omega} \text{~can be positive or negative}.$$
\end{enumerate}
